\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{array}


\makeatletter

\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\makeatother
\usepackage{lineno,setspace}
\usepackage{fancyhdr}
\usepackage{}
\pagestyle{fancy}
\usepackage[small,compact]{titlesec}
\usepackage[small,it]{caption}
\addtolength{\belowcaptionskip}{-3mm}
\addtolength{\abovecaptionskip}{-3mm}
\usepackage{hanging}
\usepackage{babel}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}


\makeatother

\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\lfoot{Monroe CV}
%\cfoot{CV}
\rfoot{\thepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin {center}
{\huge J Grey Monroe}\tabularnewline
\vspace{1em}
\today

\vspace{1em}

\begin{tabular}{>{\raggedright}p{3in}>{\raggedleft}p{3in}}
Assistant Professor & University of California Davis\tabularnewline
 gmonroe@ucdavis.edu &  Department of Plant Sciences \tabularnewline
Phone: 919.810.8800 & Davis, California\tabularnewline
\end{tabular}
\href{www.monroelab.org}{monroelab.org}
\end{center}
\vspace{-1em}

\rule[0.5ex]{1\columnwidth}{0.5pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vspace{-.5ex}
\subsubsection*{EDUCATION}
\vspace{-0.5ex}

\hspace{1.0em} PhD, Ecology
\hfill
2014 - 2019
\par
\hspace*{2.0em} Colorado State University, Fort Collins \\
\hspace*{2.0em} Advisor: John K. McKay \\
\hspace*{2.0em} Dissertation: Causes and consequences of plant climate adaptation
\\
\vspace{-0.5ex}\par

\hspace{1.0em} BSc Biology, \emph{cum laude}
\hfill
2008 - 2012
\par
\hspace*{2.0em} Appalachian State University \\
\hspace*{2.0em} Advisor: Matt Estep \\
\hspace*{2.0em} Concentration: Evolution of centromeres in the \textit{Andropogoneae} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{EMPLOYMENT}
\vspace{-0.5ex}\par

\hspace{1.0em} Assistant Professor of Climate Adaptation and Plant Genomics
\hfill
July 2020
\vspace{-0.5ex}\par
\hspace{2.0em} University of California, Davis
\vspace{-0.5ex}\par
\hspace{2.0em} Department of Plant Sciences, Davis, USA
\hfill
\vspace{0.5em}\par

\hspace{1.0em} Post Doctoral Fellow, Advisor - Detlef Weigel
\hfill
2019-2020
\vspace{-0.5ex}\par
\hspace{2.0em} Max Planck Institute for Developmental Biology
\vspace{-0.5ex}\par
\hspace{2.0em} Department of Molecular Biology - Adaptation to changes, Tubingen, Germany
\hfill
\vspace{0.5em}\par

\hspace{1.0em} Data Consultant 
\hfill
2017 - 2019
\vspace{-0.5ex}\par
\hspace{2.0em} New West Genetics, USA
\vspace{-0.5ex}\par
\hspace{2.0em} Max Planck Society, Germany
\vspace{-0.5ex}\par
\hspace{2.0em} United States Geological Survey, USA
\hfill
\vspace{0.5em}\par

\hspace{1.0em} CO-OP in Plant Breeding and Genetics
\hfill
2016 - 2017
\vspace{-0.5ex}\par
\hspace{2.0em} Cargill
\vspace{-0.5ex}\par
\hspace{2.0em} Specialty Seeds and Oil Innovation Center, Fort Collins, CO
\vspace{0.5em}\par

\hspace{1.0em} Research Assistant
\hfill
2013 - 2014
\vspace{-0.5ex}\par
\hspace{2.0em} Duke University, Durham, NC
\vspace{-0.5ex}\par
\hspace{2.0em} Herman Staats Lab, Pathology Dept

\vspace{0.5em}\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{PUBLICATIONS}
\vspace{-0.5ex}
\begin{hangparas}{.5in}{1}

\textbf{\textit{Pre-Prints}}\par
\hspace{1em} \textbf{Monroe JG}, Cai H, Des Marais DL. 2020. Trait plasticity and covariance along a continuous soil moisture gradient. \textit{bioRxiv}. doi:10.1101/2020.02.17.952853

\textbf{\textit{In Press}}\par
\hspace{1em} Baggs EL, \textbf{Monroe JG}, Thanki AS, OGrady R, Schudoma C, Haerty W, Krasileva KV. 2020. Convergent loss of an EDS1/PAD4 signaling pathway in several plant lineages reveals co-evolved components of plant immunity and drought response. \textit{The Plant Cell}

\textbf{\textit{Published}}\par

\hspace{1em} Togninalli M, Serren U, Freudenthal JA,  \textbf{Monroe JG}, Meng D, Nordborg M, Weigel D, Borgwardt K, Korte A, Grimm DG. 2019. AraPheno and the AraGWAS Catalog 2020: A major database update including RNA-Seq and knockout mutation data for Arabidopsis thaliana. \textit{Nucleic Acids Research}. 
\vspace{1ex}\par
\hspace{1em} Mason CM, Lascaleia M, De La Pascua1 D, \textbf{Monroe JG},  Goolsby EW. 2019. Learning from dynamic traits: Seasonal shifts and ecophysiological tradeoffs across scales from macroevolutionary to intra-individual. \textit{International Journal of Plant Sciences}. 
\vspace{1ex}\par
\hspace{1em} Lawrence C, Beem-Miller J, Hoyt A, \textbf{Monroe JG},  29 others. 2019. An open source database for the synthesis of soil radiocarbon data: ISRaD version 1.0. \textit{Earth System Science Data Discussions}.
\vspace{1ex}\par
\hspace{1em} \textbf{Monroe JG}, Gill B, Turner KT, McKay JK. 2019. Drought regimens predict life history strategies in \textit{Heliophila}. \textit{New Phytologist}. doi.org/10.1111/nph.15919
\vspace{1ex}\par
\hspace{1em} \textbf{Monroe JG}, Powell T, Price N, Howard A, Evans K, Mullen JL, Lovell JT, McKay JK. 2018. Drought adaptation in \textit{Arabidopsis thaliana} by extensive genetic loss-of-function. \textit{eLife}. doi: 10.7554/eLife.41038
\vspace{1ex}\par
\hspace{1em} Endriss SB, Vahsen ML, Bitume EV, \textbf{Monroe JG}, Turner KG, Norton AP, Hufbauer RA. 2018. The importance of growing up: juvenile environment influences dispersal of individuals and their neighbors. \textit{Ecology Letters}. 22:45-55
\vspace{1ex}\par
\hspace{1em} Dittberner H, Korte A, Mettler-Altman T, Weber A, \textbf{Monroe JG}, de Meaux J. 2018. Natural variation in stomata size contributes to the local adaptation of water-use efficiency in \textit{Arabidopsis thaliana}. \textit{Molecular Ecology}. DOI 10.1111/mec.14838.
\vspace{1ex}\par
\hspace{1em}  Price N, Moyers BT, Lasky JR, \textbf{Monroe JG}, Mullen JL, Lopez L, Oakley CG, Lin J, Agren J, Schrider DR, Kern AD, McKay JK. 2018. Combining population genomics and fitness QTL to identify the genetics of local adaptation in \textit{Arabidopsis thaliana}. \textit{Proceedings of the National Academy of Sciences}. 115:5028-5033
\vspace{1ex}\par
\hspace{1em}  \textbf{Monroe JG}, Markman DW, Beck WS, Felton AJ, Vahsen ML, Pressler Y. 2018. Eco-evolutionary Dynamics of Carbon Cycling in the Anthropocene. \textit{Trends in Ecology and Evolution}. 33:213-225.
\vspace{1ex}\par
\hspace{1em}  \textbf{Monroe JG}, Allen ZA, Tanger P, Mullen JL, Lovell JT, Moyers BT, Whitley D, McKay JK. 2017. \textit{TSPmap}, a tool making use of traveling salesperson problem solvers in the efficient and accurate construction of high-density genetic linkage maps. \textit{BioData Mining}. DOI 10.1186/s13040-017-0158-0.
\vspace{1ex}\par
\hspace{1em} Rockenbach K, Havrid JC, \textbf{Monroe JG}, Triant DA, Taylor DR, Sloan DB. 2016. Positive Selection in Rapidly Evolving Plastid-Nuclear Enzyme Complexes. \textit{Genetics} 204:1507-1522.
\vspace{1ex}\par
\hspace{1em} \textbf{Monroe JG}, McGovern C, Lasky J, Beck J, Grogan K, McKay JK. 2016. Adaptation to warmer climates by parallel functional evolution of \textit{CBF} genes in \textit{Arabidopsis thaliana}. \textit{Molecular Ecology} 15:3632-3644.
\vspace{1ex}\par
\hspace{1em} Mojica JP, Mullen J, Lovell JT, \textbf{Monroe JG}, Paul JR, Oakley CG, McKay JK. 2016. Genetics of water use physiology in locally adapted \textit{Arabidopsis thaliana}. \textit{Plant Science}  251:12-22.
\vspace{1ex}\par
\hspace{1em} Zhu M, \textbf{Monroe JG}, Suhail Y, Villiers F, Mullen J, Pater D, Hauser F, Jeon BW, Bader JS, Kwak JM, Schroeder JI, McKay JK, Assman SM. 2016. Molecular and Systems Approaches towards Drought-tolerant Canola Crops. \textit{New Phytologist} 210:1169-1189.
\end{hangparas}
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{FELLOWSHIPS}
\vspace{-0.5ex}
\hspace*{1.0em} Vice President of Research Fellowship, CSU (\$4,000)
\hfill
2017 - 2018
\vspace{1ex}\\
\hspace*{1.0em} USDA-NIFA National Needs Fellowship (\$138,000)
\hfill
2015 - 2018
\vspace{1ex}\\
\hspace*{1.0em} Program in Molecular Plant Biology Fellowship, CSU (\$39,000)
\hfill
2014 - 2015
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{GRANTS}
\vspace{-0.5ex}
\hspace*{1.0em}Co-PI, Aligning the Food System Symposium, UCD World Food Center (\$25,000)
\hfill
2020\\
\hspace*{2.0em} Title: Catalyzing Adaptive and Resilient Food Systems
\vspace{1ex}\\
\hspace*{1.0em} PI, Research Mentoring to Advance Inclusivity in STEM, CSU (\$1,160)
\hfill
2018\vspace{1ex}\\
\hspace*{1.0em} Co-PI, Doctoral Dissertation Improvement Grant, NSF (\$19,760)
\hfill
2017\\
\hspace*{2.0em} Title: The evolution of plant drought tolerance and gene function across\\
\hspace*{2.0em} historic drought frequency gradients
\vspace{1ex}\\
\hspace*{1.0em} PI, Evo-Devo-Eco Network Grant, Harvard University (\$3,000)
\hfill
2016\\
\hspace*{2.0em} Title: Variation  in  developmental  and  physiological  responses  to  a  gradient\\ \hspace*{2.0em} of water availability in \textit{Brachypodium}
\vspace{1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{AWARDS AND HONORS}
\vspace{-0.5ex}
\hspace*{1.0em} Rising Star in Organismal Botany, SICB \hfill2020
\vspace{1ex}\\
\hspace*{1.0em} Graduate Degree Program in Ecology Travel Award, CSU \hfill2018
\vspace{1ex}\\
\hspace*{1.0em} Graduate Degree Program in Ecology Travel Award, CSU \hfill2017
\vspace{1ex}\\
\hspace*{1.0em} Ralph Baker Graduate Student Award for Research Excellence, CSU 
\hfill
2017
\vspace{1ex}\\
\hspace*{1.0em} NSF Graduate Research Fellowship Honorable Mention
\hfill
2016
\vspace{1ex}\\
\hspace*{1.0em} Ralph Baker Graduate Student Award for Research Excellence, CSU 
\hfill
2016
\vspace{1ex}\\
\hspace*{1.0em} PMPB Research and Scholarly Excellence Award, CSU 
\hfill
2015
\vspace{1ex}\\
\hspace*{1.0em} NSF Graduate Research Fellowship Honorable Mention
\hfill
2015
\vspace{1ex}\\
\hspace*{1.0em} GDPE Research and Scholarly Excellence Award, CSU
\hfill
2014
\vspace{1ex}\\
\hspace*{1.0em}  Frontiers and Techniques in Plant Science Workshop Scholarship,\\
\hspace*{1.0em} Cold Spring Harbor Laboratory 
\hfill
2014
\vspace{1ex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{WORKSHOPS, WORKING GROUPS AND TRAINING}
\vspace{-0.5ex}
\hspace*{1.0em} Research Intern, Drought Physiology group
\hfill
2018
\vspace{1ex}\\
\hspace*{2.0em}  International Rice Research Institute, Los Banos, Philippines
\vspace{1ex}\\
\hspace*{1.0em} Genotype $\times$ Environment Interactions Workshop, participant
\hfill
2015
\vspace{1ex}\\
\hspace*{2.0em}  Wageningen University, Wageningen, Netherlands
\vspace{1ex}\\
\hspace*{1.0em} microMORPH Phenotypic Plasticity Workshop, invited participant
\hfill
2015
\vspace{1ex}\\
\hspace*{2.0em}  Harvard University Arnold Arboretum, Boston, MA
\vspace{1ex}\\
\hspace*{1.0em} Plasticity and Novel Environments Working Group, invited participant
\hfill
2015
\vspace{1ex}\\
\hspace*{2.0em}  National Evolutionary Synthesis Center, Durham, NC
\vspace{1ex}\\
\hspace*{1.0em} Frontiers and Techniques in Plant Science, invited participant
\hfill
2014
\vspace{1ex}\\
\hspace*{2.0em}  Cold Spring Harbor Laboratory, Cold Spring Harbor, NY
\vspace{1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{PRESENTATIONS}
\vspace{-0.5ex}

\hspace*{1.0em}University of Bern \hfill 2020 \par
\hspace*{2.0em}Bern, Switzerland \par\vspace{0.5ex}

\hspace*{1.0em}University of Tubingen \hfill 2020 \par
\hspace*{2.0em}Tubingen, Germany \par\vspace{0.5ex}

\hspace*{1.0em}Carnegie Institute, Stanford University \hfill 2020 \par
\hspace*{2.0em}Stanford, California \par\vspace{0.5ex}

\hspace*{1.0em}Society for Integrative and Comparative Biology \hfill 2020 \par
\hspace*{2.0em}Austin, Texas \par\vspace{0.5ex}

\hspace*{1.0em}Climate Summit of Generations \hfill 2019 \par
\hspace*{2.0em}Hamburg, Germany \par\vspace{0.5ex}

\hspace*{1.0em}Plant Genome Evolution \hfill 2019 \par
\hspace*{2.0em}Sitges, Spain \par\vspace{0.5ex}

\hspace*{1.0em}International Center for Tropical Agriculture  \hfill 2019 \par
\hspace*{2.0em}Palmira, Colombia \par\vspace{0.5ex}

\hspace*{1.0em}International Plant and Animal Genome Conference  \hfill 2019 \par
\hspace*{2.0em}San Diego, California \par\vspace{0.5ex}

\hspace*{1.0em}Max Planck Institute of Plant Breeding  \hfill 2018 \par
\hspace*{2.0em}Cologne, Germany \par\vspace{0.5ex}

\hspace*{1.0em}Department of Biology, University of Cologne  \hfill 2018 \par
\hspace*{2.0em}Cologne, Germany \par\vspace{0.5ex}

\hspace*{1.0em}Max Planck Institute of Developmental Biology  \hfill 2018 \par
\hspace*{2.0em}Tubingen, Germany  \par\vspace{0.5ex}

\hspace*{1.0em}Lasky Lab, Department of Biology, Pennsylvania State Univeristy  \hfill 2018 \par
\hspace*{2.0em}State College, PA \par\vspace{0.5ex}

\hspace*{1.0em}Emerging Technologies to Prevent Future Famines Symposium  \hfill 2018 \par
\hspace*{2.0em}Fort Collins, CO \par\vspace{0.5ex}

\hspace*{1.0em}Breeding and Strategic Innovation Seminar, International Rice Research Institute  \hfill 2018 \par
\hspace*{2.0em}Los Banos, Philippines \par\vspace{0.5ex}

\hspace*{1.0em}Department of Biology, Australian National University  \hfill 2018 \par
\hspace*{2.0em}Canberra, Australia \par\vspace{0.5ex}

\hspace*{1.0em}Population Biology Seminar,  Duke University  \hfill 2017 \par
\hspace*{2.0em}Durham, NC \par\vspace{0.5ex}

\hspace*{1.0em}Department of Biology. Appalachian State University  \hfill 2017 \par
\hspace*{2.0em}Boone, NC  \par\vspace{0.5ex}

\hspace*{1.0em}Dupont-Pioneer Drought Tolerance Symyposium\hfill 2017 \par
\hspace*{2.0em}Fort Collins, CO \par\vspace{0.5ex}

\hspace*{1.0em}Evolution\hfill 2017 \par
\hspace*{2.0em}Portland, OR \par\vspace{0.5ex}

\hspace*{1.0em}Front Range Student Ecology Symposium\hfill 2017 \par
\hspace*{2.0em}Fort Collins, CO \par\vspace{0.5ex}

\hspace*{1.0em}Three Minute Thesis Competition\hfill 2017 \par
\hspace*{2.0em}Fort Collins, CO. \par\vspace{0.5ex}

\hspace*{1.0em}Graduate Student Showcase\hfill 2016 \par
\hspace*{2.0em}Fort Collins, CO \par\vspace{0.5ex}

\hspace*{1.0em}Genomics of Adaptation to Human Contexts\hfill 2016 \par
\hspace*{2.0em}Fort Collins, CO \par\vspace{0.5ex}

\hspace*{1.0em}Evolution\hfill 2016 \par
\hspace*{2.0em}Austin, TX \par\vspace{0.5ex}

\hspace*{1.0em}Guild of Rocky Mountain Ecologists and Evolutionary Biologists \hfill 2015 \par
\hspace*{2.0em}Boulder, CO \par\vspace{0.5ex}

\hspace*{1.0em}Evolution \hfill 2015 \par
\hspace*{2.0em}Sao Paolo, Brazil \par\vspace{0.5ex}

\hspace*{1.0em}MicroMOPRH Phenotypic Plasticity Workshop. Harvard Arnold Arboretum  \hfill 2015 \par
\hspace*{2.0em}Boston, MA  \par\vspace{0.5ex}

\hspace*{1.0em}NESCent Plasticity and Novel Environments Working Group  \hfill 2015 \par
\hspace*{2.0em}Durham, NC \par\vspace{0.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{TEACHING}
\vspace{-0.5ex}\par
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} Drought Tolerance Breeding Workshop, CSU
\hfill
2018
\par
\vspace{0.5em}
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} Ecosystem Ecology, CSU
\hfill
2017
\par
\vspace{0.5em}
\hspace*{1.0em} Teaching Assistant
\par
\hspace*{2.0em} Molecular and General Genetics, CSU
\hfill
2017
\par
\vspace{0.5em}
\hspace*{1.0em} Assistant Instructor
\par
\hspace*{2.0em} Software Carpentry Workshop, CSU
\hfill
2016
\par
\vspace{0.5em}
\hspace*{1.0em} Guest lecturer
\par
\hspace*{2.0em} ECOL 592: Principles of Data Visualization Using R and ggplot2, CSU
\hfill
2016
\vspace{0.5em}
\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{MENTORSHIP}
\vspace{-0.5ex}\par
\hspace*{1.0em} Sebastian Vorbrugg -  genome graph construction and GWAS
\hfill
2019\\
\hspace*{2.0em} Max Planck Institute for Developmental Biology

\hspace*{1.0em} Thanvi Srikant - epigenetic impacts on genetic evolution
\hfill
2019\\
\hspace*{2.0em} Max Planck Institute for Developmental Biology

\hspace*{1.0em} Karter Johansen -  theoretical population genetics of poly-allelic adaptation
\hfill
2017\\
\hspace*{2.0em} Colorado State University

\hspace*{1.0em} Tyler Powell - reverse genetics of adaptive loss-of-function alleles
\hfill
2017\\
\hspace*{2.0em} Colorado State University

\hspace*{1.0em} Julio Flores - awarded scholarship for research on plant ecotoxicology
\hfill
2014 - 2015\\
\hspace*{2.0em} Poudre High School
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{ACADEMIC SERVICE}
\vspace{-0.5ex}\par

\hspace*{1.0em} Lecturer: Implicit Bias
\par
\hspace*{2.0em} CSU Research Mentoring to Advance Inclusiveness in Science
\hfill
2018

\hspace*{1.0em} Assistant organizer
\par
\hspace*{2.0em} BSURE Undergraduate Summer Mentorship Program
\hfill
2017

\hspace*{1.0em} Co-organizer
\par
\hspace*{2.0em} Drought Tolerance in Agriculture and Natural Ecosystems Symposium
\hfill
2017
\hspace*{2.0em} DuPont-Pioneer and Colorado State University
\par
\vspace{0.5em}
\hspace*{1.0em} Assistant Organizer
\par
\hspace*{2.0em} Front Range Student Ecology Symposium
\hfill
2015, 2017\\
\hspace*{2.0em} Graduate Degree Program in Ecology and Colorado State University
\par
\hspace*{1.0em} Peer Review
\par
\hspace*{2.0em} Evolution, New Phytologist, Theoretical and Applied Genetics, Evolutionary Applications, Scientific Reports, PLoS One, Molecular Ecology, Nucleic Acids Research, Plant Cell and Enviroment, The Plant Journal, Genes

\vspace{0.5em}\par


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{SOFTWARE DEVELOPMENT}
\vspace{-0.5ex}

\begin{hangparas}{.5in}{1}
\hspace{1em}\textbf{J Grey Monroe}. ISRaD: R package for interacting with International Soil Radiocarbon Database\vspace{0.5ex}\par
\hspace{1em}\textbf{J Grey Monroe}. genemodel: Gene Model Plotting in R. R package version 1.1.0.
  https://CRAN.R-project.org/package=genemodel
\vspace{0.5ex}\par
\hspace{1em}\textbf{J Grey Monroe}., Zachary Allen, Paul Tanger, Brook Moyers and Jack Mullen (2016). TSPmap: A Method Making Use of Traveling Salesperson Problem Solvers in the Construction of Genetic Linkage Maps. R package version 0.0.0.9000. \\https://github.com/mckaylab/tspmap

\end{hangparas}

\end{document}
